---
title: "EPA Whole Effluent Toxicity analysis"
format:
  html:
    embed-resources: true
    toc: true
    theme: flatly
execute:
  echo: false
  warning: false
---

```{r}
#| label: setup
library(toxstats)
library(shinytoxstats)
analysis <- readRDS("analysis.rds")
fit <- analysis$fit
```

*Produced by `shinytoxstats` on `r format(Sys.time(), "%d %B %Y at %H:%M")`.*

## What was analysed

```{r}
#| label: design
fit$data
```

`r if (nrow(fit$excluded)) "The following concentrations were excluded from the hypothesis test, and are retained for point estimation as section 9.5.2 requires." else ""`

```{r}
#| label: excluded
#| eval: !expr nrow(fit$excluded) > 0
knitr::kable(fit$excluded)
```

## How the test was chosen

The table below is the record of every branch point of the EPA flowchart: the
question asked, the statistic that answered it, the consequence, and the
section of the manual that justifies it. A reviewer can check this line by line
against the manual.

```{r}
#| label: trail
trail <- decisions(fit)
knitr::kable(
  trail[, c("step", "question", "outcome", "reference")],
  col.names = c("Step", "Question", "Outcome", "Manual section")
)
```

```{r}
#| label: override
#| eval: !expr isTRUE(fit$overridden)
```

`r if (isTRUE(fit$overridden)) paste0("**The selected test was overridden.** The flowchart selected ", fit$selected, ". This result is not the analysis the EPA manual prescribes for these data.") else ""`

## Endpoints

```{r}
#| label: endpoints
out <- as.data.frame(fit)
numeric <- vapply(out, is.numeric, logical(1))
out[numeric] <- lapply(out[numeric], signif, digits = 5)
knitr::kable(out)
```

## Concentration-response

```{r}
#| label: plot
#| fig-height: 4
#| fig-width: 7
plot_response(fit)
```

## Comparisons

```{r}
#| label: comparisons
comparisons <- fit$comparison$comparisons
numeric <- vapply(comparisons, is.numeric, logical(1))
comparisons[numeric] <- lapply(comparisons[numeric], signif, digits = 5)
knitr::kable(comparisons)
```

## Reproducing this analysis

Running the following in R gives exactly the result above, without this
application.

```{r}
#| label: code
#| echo: false
#| comment: ""
cat(analysis$code, sep = "\n")
```

## Provenance

```{r}
#| label: provenance
knitr::kable(
  data.frame(
    Item = c("toxstats", "shinytoxstats", "R", "Flowchart"),
    Value = c(
      as.character(utils::packageVersion("toxstats")),
      as.character(utils::packageVersion("shinytoxstats")),
      R.version.string,
      fit$flowchart
    )
  )
)
```

The `toxstats` package targets the EPA method manuals rather than the ToxCalc
software, and documents every point at which the manuals are ambiguous or
internally inconsistent. See its vignette, *Recreating ToxCalc: methods and
decisions*.
